---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

source("functions.R")
```

\par\centering{\LARGE{Reiley Thomas Bergin, Ph.D.}}
\par\centering{Athletic Training and Clinical Nutrition}
\vspace{-5pt}
\par\centering{University of Kentucky}
\vspace{-5pt}
\par\centering{Sports Medicine Research Institute (SMRI)}
\vspace{-5pt}
\par\centering{720 Sports Center Dr., Lexington, KY 40536}
\vspace{-5pt}
\par\centering{{\large\Telefon} +1 (859) 323-9832}
\vspace{-5pt}
\par\centering{{\large\Letter} reiley.bergin@uky.edu}
<!--
\vspace{-5pt}
\par\centering{\href{http://www.rtbergin.com}{www.rtbergin.com}}
-->

# Education

\setlength{\tabcolsep}{4pt}
\vspace{-10pt}
\begin{longtable}{lll}

    2024 & University of Kentucky, Lexington, KY & Ph.D. Rehabilitation Sciences\\

    \multicolumn{3}{p{\dimexpr\textwidth-2\tabcolsep}}{\small \raggedright Dissertation: \emph{Using Inertial Measurement Units (IMUs) to Assess Fatigue-\-Related Changes in Running: Applications in Training Load Management}}\\
    
    \multicolumn{3}{l}{Doctoral Committee: \emph{Nick Heebner, Stuart Best, Matt Hoch, \& Josh Winters}}\\[5pt]
    
    2016 & Florida State University, Tallahassee, FL & M.S. Exercise Physiology\\

    2014 & Indiana University, Bloomington, IN & B.S. Biology\\[5pt]

\end{longtable}

\vspace{-10pt}

# Professional Experiences

\vspace{-10pt}
\begin{longtable}{llp{15cm}}
2020 - 2024 & \textbf{University of Kentucky}, Lexington, KY & \\
 & Research Analyst Principal, Sports Medicine Research Institute (SMRI)\\[5pt]
2017 - 2020 & \textbf{University of Kentucky}, Lexington, KY & \\
 & Graduate Research Assistant, Sports Medicine Research Institute (SMRI)\\[5pt]
2016 & \textbf{Florida State University}, Tallahassee, FL & \\
 & Graduate Assistant, Athletic Department\\[5pt]
2015 & \textbf{University of Notre Dame}, South Bend, IN & \\
 & Sports Science Intern, Athletic Department\\
\end{longtable}

\vspace{-10pt}

# Academic Appointments

\vspace{-10pt}
\begin{longtable}{llp{15cm}}
2024 - Present & \textbf{University of Kentucky}, Lexington, KY & \\
 & Assistant Professor, Athletic Training and Clinical Nutrition\\[5pt]
\end{longtable}

\vspace{-10pt}

# Teaching Activity

## Courses Taught at University of Kentucky:

```{r}
df <- get_cv_sheet('classes') %>% 
    mutate(
      course = paste0(number, ": ", name), 
      num = paste(responses, '/', enrolled), 
      score = paste(inst_mean, '/', dept_mean),
      semester = ifelse(semester == 'S20', 'S20$^†$', semester)
    ) %>% 
    select(
      `Sem.` = semester,
      Course = course,
      Level = level, 
      `N. Resp. / N. Enrolled` = num,
      `Instr. FCE* / Dept Mean` = score
    ) 

df %>% 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "") %>% 
  column_spec(4, width = "1.8cm") %>% 
  column_spec(5, width = "2cm") 
  #footnote(symbol = c("", ""))
```

# Research and/or Creative Productivity

## Publications

<!-- Set spacing in between list -->

\apptocmd{\tightlist}{\setlength{\itemsep}{4pt}}{}{}

ORCID: \href{https://orcid.org/0009-0002-5771-033X}{0009-0002-5771-033X} | [Google Scholar Profile](https://scholar.google.com/citations?user=o6oB6AwAAAAJ&hl=en)

\underline{Underline} indicates advisee; \* graduate student, \*\*undergraduate student

### A. Refereed/Peer reviewed

#### 1. Published Journal Articles

```{r}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal), '', paste0('_', journal, '_.')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('DOI: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi)
  ) %>% 
  arrange(desc(pub_date))
```

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "peer_rev_pub_article")
```

<!--
#### 2. Publications Submitted
-->
```{r}

# UPDATE once I have some publications in review

# #| results: asis
 
# make_ordered_list_filtered(pubs, "peer_review_article_in_review")
```


#### 2. Theses

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "dissertation")
```

#### 3. Abstracts/Peer-Reviewed Original Research

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "peer_rev_abstract")
```