---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

source("functions.R")
```

\par\centering{\LARGE{Reiley Thomas Bergin, Ph.D.}}
\par\centering{Athletic Training and Clinical Nutrition}
\vspace{-5pt}
\par\centering{University of Kentucky}
\vspace{-5pt}
\par\centering{Sports Medicine Research Institute (SMRI)}
\vspace{-5pt}
\par\centering{720 Sports Center Dr., Lexington, KY 40536}
\vspace{-5pt}
\par\centering{{\large\Telefon} +1 (859) 323-9832}
\vspace{-5pt}
\par\centering{{\large\Letter} reiley.bergin@uky.edu}
<!--
\vspace{-5pt}
\par\centering{\href{http://www.rtbergin.com}{www.rtbergin.com}}
-->

# Education

\setlength{\tabcolsep}{4pt}
\vspace{-10pt}
\begin{longtable}{lll}

    2024 & University of Kentucky, Lexington, KY & Ph.D. Rehabilitation Sciences\\

    \multicolumn{3}{p{\dimexpr\textwidth-2\tabcolsep}}{\small \raggedright Dissertation: \emph{Using Inertial Measurement Units (IMUs) to Assess Fatigue-\-Related Changes in Running: Applications in Training Load Management}}\\
    
    \multicolumn{3}{l}{Doctoral Committee: \emph{Nick Heebner, Stuart Best, Matt Hoch, \& Josh Winters}}\\[5pt]
    
    2016 & Florida State University, Tallahassee, FL & M.S. Exercise Physiology\\

    2014 & Indiana University, Bloomington, IN & B.S. Biology\\[5pt]

\end{longtable}

\vspace{-10pt}

# Professional Experiences

\vspace{-10pt}
\begin{longtable}{llp{15cm}}
2024 - Present & \textbf{University of Kentucky}, Lexington, KY & \\
 & Assistant Professor, Athletic Training and Clinical Nutrition\\[5pt]
2024 - Present & \textbf{University of Kentucky}, Lexington, KY & \\
 & Assistant Professor, Athletic Training and Clinical Nutrition\\[5pt]
2024 - Present & \textbf{University of Kentucky}, Lexington, KY & \\
 & Assistant Professor, Athletic Training and Clinical Nutrition\\[5pt]
2024 - Present & \textbf{University of Kentucky}, Lexington, KY & \\
 & Assistant Professor, Athletic Training and Clinical Nutrition\\
\end{longtable}

\vspace{-10pt}

# Academic Appointments

\vspace{-10pt}
\begin{longtable}{llp{15cm}}
2024 - Present & \textbf{University of Kentucky}, Lexington, KY & \\
 & Assistant Professor, Athletic Training and Clinical Nutrition\\[5pt]
\end{longtable}

\vspace{-10pt}

# Teaching Activity

## Courses Taught at University of Kentucky:

```{r}
df <- get_cv_sheet('classes') %>% 
    mutate(
      course = paste0(number, ": ", name), 
      num = paste(responses, '/', enrolled), 
      score = paste(inst_mean, '/', dept_mean),
      semester = ifelse(semester == 'S20', 'S20$^†$', semester)
    ) %>% 
    select(
      `Sem.` = semester,
      Course = course,
      Level = level, 
      `N. Resp. / N. Enrolled` = num,
      `Instr. FCE* / Dept Mean` = score
    ) 

df %>% 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "") %>% 
  column_spec(4, width = "1.8cm") %>% 
  column_spec(5, width = "2cm") 
  #footnote(symbol = c("", ""))
```

# Research and/or Creative Productivity

## Publications

<!-- Set spacing in between list -->

\apptocmd{\tightlist}{\setlength{\itemsep}{4pt}}{}{}

<!--
ORCID: \href{https://--- ADD LATER ---} \| [Google Scholar Profile](https://--- ADD LATER ---)
-->

\underline{Underline} indicates advisee; \* graduate student, \*\*undergraduate student

### A. Refereed/Peer reviewed

#### 1. Published Journal Articles

```{r}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal), '', paste0('_', journal, '_.')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('DOI: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi)
  ) %>% 
  arrange(desc(pub_date))
```

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "peer_reviewed")
```

#### 2. Publications Submitted or in Preparation

```{r}
#| results: asis
 
make_ordered_list_filtered(pubs, "working")
```

#### 3. Theses

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "theses")
```

#### 4. Abstracts/Peer-Reviewed Original Research


<!-- \newpage -->

<!-- # References -->

<!-- \begin{longtable}{p{7cm} p{8.6cm}} -->

<!--   \textbf{Erica R.H. Fuchs} & \textbf{Jeremy J. Michalek} \\ -->

<!--   Professor & Professor \\ -->

<!--   Department of Engineering and Public Policy & Department of Engineering and Public Policy \\ -->

<!--   Carnegie Mellon University & Department of Mechanical Engineering \\ -->

<!--   Baker Hall 131E & Carnegie Mellon University \\ -->

<!--   5000 Forbes Avenue & Scaife Hall 324 \\ -->

<!--   Pittsburgh, PA 15213 & 5000 Forbes Avenue \\ -->

<!--   Phone: +1 (412) 268-1877 & Pittsburgh, PA 15213 \\ -->

<!--   Email: erhf@andrew.cmu.edu & Phone: +1 (412) 268-3765 \\ -->

<!--   & Email: jmichalek@cmu.edu \\ -->

<!--   &  \\ -->

<!--   \textbf{Elea McDonnell Feit} & \textbf{Valerie J. Karplus}\\ -->

<!--   Associate Professor of Marketing & Associate Professor\\ -->

<!--   LeBow College of Business & Department of Engineering and Public Policy\\ -->

<!--   Drexel University & Carnegie Mellon University\\ -->

<!--   Gerri C. LeBow Hall 828 & Scott Hall 5113\\ -->

<!--   3141 Chestnut Street & 5000 Forbes Avenue\\ -->

<!--   Philadelphia, PA 19104 & Pittsburgh, PA 15213\\ -->

<!--   Phone: +1 (215) 571-4054 & Email: vkarplus@andrew.cmu.edu \\ -->

<!--   Email: efeit@drexel.edu & \\ -->

<!--   &  \\ -->

<!--   \textbf{Peter Fox-Penner} & \textbf{Zoe Szajnfarber} \\ -->

<!--   Director, Institute for Sustainable Energy & Professor \& Department Chair\\ -->

<!--   Questrom School of Business & Engineering Management and Systems Engineering\\ -->

<!--   Boston University & George Washington University\\ -->

<!--   Rafik B. Hariri Building, Room 514A & Science \& Engineering Hall 2670\\ -->

<!--   595 Commonwealth Ave. & 800 22nd Street, NW\\ -->

<!--   Boston, MA 02215 & Washington, DC 20052 \\ -->

<!--   Phone: +1 (617) 353-4298 & Phone: +1 (202) 994-7153\\ -->

<!--   Email: pfoxfp@bu.edu & Email: zszajnfa@gwu.edu\\ -->

<!-- \end{longtable} -->
